Supporting Information

### 2018-03-20 SupportingInformation.Rmd
activate Taylors law section

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True
link-citations: true

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
#source("TaylorsLawTools.R")

#We are only doing spatial taylor's law because we know a priori temporal
#won't give anything interesting for the surrogates we use

#kend.stats.res<-list()
#kend.points.res<-list()
#spea.stats.res<-list()
#spea.points.res<-list()
#for (counter in 1:length(kend.surrog))
#{
 # ks<-kend.surrog[[counter]]
#  ss<-spea.surrog[[counter]]
 # kend.stats.res[[counter]]<-matrix(NA,5,numdat)
#  spea.stats.res[[counter]]<-matrix(NA,5,numdat)
 # kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
  #spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
  #for (sc in 1:numdat)
  #{
   # khold<-tl_stats(ks[,,sc])
  #  kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
   # rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
    #kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)

    #shold<-tl_stats(ss[,,sc])
    #spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
    #rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
    #spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
  #}
#}
#names(kend.stats.res)<-names(kend.surrog)
#names(kend.points.res)<-names(kend.surrog)
#names(spea.stats.res)<-names(spea.surrog)
#names(spea.points.res)<-names(spea.surrog)

#DAN: now you want to compare whether tl held, and the slope (statistically and visually)
#across the different elements of kend.XX.res and spea.XX.res. See drawing of a figure layout on desk.

>>>>

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True
link-citations: True

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("TaylorsLawTools.R")
# 
# #We are only doing spatial taylor's law because we know a priori temporal
# #won't give anything interesting for the surrogates we use
# 
 kend.stats.res<-list()
 kend.points.res<-list()
 spea.stats.res<-list()
 spea.points.res<-list()
 for (counter in 1:length(kend.surrog))
 {
   ks<-kend.surrog[[counter]]
   ss<-spea.surrog[[counter]]
   kend.stats.res[[counter]]<-matrix(NA,5,numdat)
   spea.stats.res[[counter]]<-matrix(NA,5,numdat)
   kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
   spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
   for (sc in 1:numdat)
   {
     khold<-tl_stats(ks[,,sc])
     kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
     rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
     kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)
# 
     shold<-tl_stats(ss[,,sc])
     spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
     rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
     spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
   }
 }
 names(kend.stats.res)<-names(kend.surrog)
 names(kend.points.res)<-names(kend.surrog)
 names(spea.stats.res)<-names(spea.surrog)
 names(spea.points.res)<-names(spea.surrog)
```

<!--Now make some plots-->
```{r taylor_plots, echo=T}
##plot TL for clayton
xlimits<-range(kend.points.res[[1]][,1,],kend.points.res[[2]][,1,],kend.points.res[[3]][,1,],kend.points.res[[4]][,1,])
ylimits<-range(kend.points.res[[1]][,2,],kend.points.res[[2]][,2,],kend.points.res[[3]][,2,],kend.points.res[[4]][,2,])
par(mfrow=c(1,1))
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
##plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```
